Thesis Project Proposal Meeting

### 2020-09-13 thesis proposal .Rmd
final proposal updates

# Goals for today's meeting 
1. Discuss project proposal below and the different ways to go
2. Discuss how to design proper search term parameters that provides big picture but managable study count
3. Outline timeline for regular meetings and when milestones for this project should accomplished
4. Discuss appropriate workflow for this project

# Main Objectives 
How is environmental variation (temperature, pH, nutrient composition) systematically studied and manipulated across organismal, population, and community ecology and how does study design influence conclusions about environmental variation compare across these bodies of literature?

Does environmental variation affect how rates scale across levels of biological organization?

@@

Ha: Short term responses to simple environmental variation manipulation is prioritized at the organismal level, long term and more complex environmental variation manipulated is prioritized at the population and community level, owing to differential experimental design and conclusions about how variation type will interact in the ecosystem.

@@

Ha2: Environmental variation alters how rates scale across levels of biological organization by influencing metabolic rate

# Methods
1. I will conduct a series of ISI literature searches to get a hollistic set of studies referencing environmental variation with selected keywords. I will then select studis based on a stricy set of criteria and enter those studies into a spreadsheet, recording relevant information (study organism, biological organization level, variation type, response variable, ).

@@

2. I will then synthesize the patterns across studies to address my main objectives. This will culminate in written document summarizing that language used in different sub disciplines as well as the similarities and differences in environmental variability.

@@

Figure 2 is a simple first pass at potentially looking about how MTE and environmental variability could interact. I'd be really interested in looking into the math for how environmental variability could alter metabolic rate and looking the relationship between body size. I think this sample figure will answer the question of whether or not environmental variability has the ability to scale with rates across levels of organization.

>>>>

# Goals for today's meeting 
1. Discuss the project proposal below and the different ways to proceed
2. Discuss how to design proper search term parameters that provide a representative but managable study count
3. Outline timeline for regular meetings and when milestones for this project should accomplished
4. Discuss appropriate workflow for this project

# Main Objectives 
1. How is environmental variation (temperature, pH, nutrient composition) systematically studied and manipulated across organismal, population, and community ecology and how does study design influence conclusions about environmental variation compare across these bodies of literature?

2. Does environmental variation affect how rates scale across levels of biological organization?

@@

Ha: Short term responses to simple environmental variation manipulation are prioritized at the organismal level, long term responses and more complex environmental variation manipulation is prioritized at the population and community level, owing to differential experimental design and conclusions about how variation type will interact in the ecosystem.

@@

Ha2: Environmental variation alters how rates scale across levels of biological organization by influencing metabolic rate.

# Methods
1. I will conduct a series of ISI literature searches to get a hollistic set of studies referencing environmental variation with selected keywords. I will then select studies based on a strict set of criteria and enter those studies into a spreadsheet, recording relevant information (study organism, biological organization level, variation type, response variable, etc.).

@@

2. I will then synthesize the patterns across studies to address my main objectives. This will culminate in a written document summarizing the language used in different sub-disciplines as well as the similarities and differences in conclusions about environmental variability.

@@

Figure 2 is a simple first pass at potentially looking about how MTE and environmental variability could interact. I'd be really interested in looking into the math for how environmental variability could alter metabolic rate and the relationship between body size. I think this sample figure could answer the question of whether or not environmental variability has the ability to scale with rates across levels of organization.
